---
title: "Data Skills Assignment"
author: "Student ID: 2597588"
date: 03/03/2025
format:
  html: 
    embed-resources: true
---
Libraries
```{r}
library(here)
library(tidyverse)
library(ggplot2)
```

Loading the data
```{r}
#The working directory may vary among different users.
accent_bc <- read_csv("datasets/uk_accents_bishop_coupland.csv")
accent_bc
```

#Visulization No. 1 (Coupland and Bishop 2004)

Calculating the mean values
```{r}
#The two mean values here will be used to indicate a specific point on the plot.
avg_x <- mean(accent_bc$Attractiveness, na.rm = TRUE)
avg_y <- mean(accent_bc$Prestige, na.rm = TRUE)
avg_x #3.891471
avg_y #3.466471
```

Scatter Plot
```{r}
ggplot(
  data = accent_bc, 
  mapping = aes(x = Attractiveness, y = Prestige)
) +
  geom_point(color = "pink", size = 1.8) +
  geom_text(aes(label = Label), vjust = -1.35, size = 1.2) +
  geom_point(data = NULL, x = avg_x, y = avg_y, color = "blue", size = 2.5, shape = 17) + 
  geom_text(x = avg_x, y = avg_y, label = "Average", vjust = 2, color = "blue", size = 1.3) + 
  geom_segment(data = NULL, x = avg_x, xend = avg_x, y = 2, yend = avg_y, 
               linetype = "dashed", color = "purple", linewidth = 0.2) + #Vertical Line
  geom_hline(yintercept = avg_y, linetype = "dashed", color = "purple", linewidth = 0.2) + #Horizontal Line
  theme_classic() +
  geom_smooth(method = "lm", se = FALSE, color = "grey", alpha = 0.5, linewidth = 0.6) +
  labs(x = "Attractiveness", y = "Prestige", subtitle = "UK Accents Coupland and Bishop 2004") +
  ggtitle("The Correlation Between Attractiveness and Prestige")
```


##Visulization No. 2 (Coupland and Bishop 2004)

Non-native Accents Data Frame
```{r}
non_native_bc <- data.frame (
  Region = c("Afro-Caribbean", "Asian/Indian", "French", "German", "Spanish"),
  Attractiveness = c(3.72, 3.21, 4.09, 3.2, 3.88),
  Prestige = c(2.9, 2.74, 3.74, 3.21, 3.29)
)
non_native_bc
accent_bc <- accent_bc |> 
  mutate(Accent_Type = ifelse(Label %in% non_native_bc$Region, "Non-Native", "Native")) |> 
  mutate(Accent_Type = as.factor(Accent_Type))
accent_bc
```

Bar chart
```{r}
ggplot(
  data = accent_bc, 
  mapping = aes(x = reorder(Label, Prestige, decreasing = TRUE), y = Prestige, fill = Accent_Type)
) +
  geom_text(aes(label = round(Prestige, 3)), hjust = -0.1, size = 2.0) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  labs(x = "Accent", y = "Prestige", title = "Prestige Ratings by Accent",
       subtitle = "UK Accent Coupland and Bishop 2004")
```


###Visulization No. 3 (Sharma et al 2019 & Coupland and Bishop 2004)
Loading Sharma et al 2019
```{r}
accent_sha <- read_csv("datasets/uk_accents_sharma_et_al.csv")
accent_sha
```

Non-native Accents Bishop
```{r}
non_native_bc <- data.frame (
  Region = c("Afro-Caribbean", "Asian/Indian", "French", "German", "Spanish"),
  Attractiveness = c(3.72, 3.21, 4.09, 3.2, 3.88),
  Prestige = c(2.9, 2.74, 3.74, 3.21, 3.29)
)
non_native_bc
accent_bc <- accent_bc |> 
  mutate(Accent_Type = ifelse(Label %in% non_native_bc$Region, "Non-Native", "Native")) |> 
  mutate(Accent_Type = as.factor(Accent_Type))
accent_bc
```

Non-native Accents Sharma
```{r}
non_native_sha <- data.frame(
  Region = c("Afro-Caribbean", "Asian/Indian","Chinese", "French", "German", "MLE", "Spanish"),
  Attractiveness = c(4.02, 3.54, 3.5, 4.57, 3.77, 3.89, 4.42),
  Prestige = c(3.52, 3.38, 3.56, 4.56, 3.88, 3.81, 4.09)
)
non_native_sha

accent_sha <- accent_sha |> 
  mutate(Accent_Type = ifelse(Label %in% non_native_sha$Region, "Non-Native", "Native")) |> 
  mutate(Accent_Type = as.factor(Accent_Type))
accent_sha
```

Mutual Non-native Accents
```{r}
mutual_non_native_accent <- data.frame (
  Region = c("Afro-Caribbean", "Asian/Indian", "French", "German", "Spanish"),
  Attrac_SHA = c(4.02, 3.54, 4.57, 3.77, 4.42),
  Year_SHA = c(2019, 2019, 2019, 2019, 2019),
  Attrac_BC = c(3.72, 3.21, 4.09, 3.2, 3.88),
  Year_BC = c(2004, 2004, 2004, 2004, 2004)
)
```

Combined Long Type Data
```{r}
mutual_long <- mutual_non_native_accent |> 
  pivot_longer(cols = c(Attrac_SHA, Attrac_BC), 
               names_to = "Attrac_Type", 
               values_to = "Attractiveness") |> 
  mutate(Year = ifelse(Attrac_Type == "Attrac_SHA", 2019, 2004))
mutual_long
```

Slope Graph
```{r}
ggplot(data = mutual_long,
       mapping = aes(x = Year, y = Attractiveness, group = Region, color = Region)) +
  geom_line(size = 0.6) +
  geom_point(size = 1.5) +
  geom_text(aes(label = round(Attractiveness, 2)), vjust = -0.8, size = 2.5) +
  geom_text(data = mutual_long |> filter(Year == 2019), 
            aes(label = Region), vjust = 1.5, hjust = 2.0, size = 2.5) +
  theme_classic() +
  labs(title = "Attractiveness of Non-native UK Accents (2004 vs. 2019)",
       subtitle = "Mutual Data from Bishop/Coupland & Sharma et al.",
       x = "Year", y = "Attractivenes") +
  scale_x_continuous(breaks = c(2004, 2019)) +
  theme(legend.position = "none")
```

Create a new file

